---
title: "Music Insights"
author: "Madeline Hoshko"
date: "September 19, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library("tidyverse")
library("dplyr")
library("readr")

survey <- read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences<-read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

First, I update the names of the columns to have a common naming style throughout and to simplify excessively long original column names. I show two possible ways to do so as we are able to use multiple ways since we are changing the names of every column.
```{r}
colnames(survey)[1]<-"time_submitted"
colnames(survey)[2]<-"pseudonym_generator"
colnames(survey)[3]<-"pseudonym"
colnames(survey)[4]<-"sex"
colnames(survey)[5]<-"academic_major"
colnames(survey)[6]<-"academic_level"
colnames(survey)[7]<-"year_born"
colnames(survey)[8]<-"instrument_list"
colnames(survey)[9]<-"favorite_song_artist"
colnames(survey)[10]<-"favorite_song"
colnames(survey)[11]<-"favorite_song_link"

colnames(survey) <- c("time_submitted", "pseudonym_generator", "pseudonym", "sex", "academic_major","academic_level", "year_born", "instrument_list", "favorite_song_artist", "favorite_song", "favorite_song_link")

colnames(survey)

colnames(preferences)[1] <- "time submitted"
colnames(preferences)[2] <- "pseudonym"

```


Creates a person table to include information from survery of each student. Then creates a song table to include information on each song from the survey. Then does the same with a ratings table where I use gather to reorganize the data to no longer be wide. 
```{r}
Person <- tibble(time_submitted=survey$time_submitted, pseudonym_generator=survey$pseudonym_generator, pseudonym=survey$pseudonym, sex=survey$sex, academic_major=survey$academic_major, academic_level=survey$academic_level, year_born=survey$year_born)

Person$academic_level <- as.factor(Person$academic_level)
Person$sex <- as.factor(Person$sex)
Person$academic_major <- as.factor(Person$academic_major)
levels(Person$academic_major)[levels(Person$academic_major)=="Computer information systems"] <- "Computer Information Systems"




Favorite_Song <- tibble(pseudonym=survey$pseudonym, song=survey$favorite_song, artist=survey$favorite_song_artist, song_link=survey$favorite_song_link)



 preferences$`time submitted` <- NULL
  Rating <- gather(preferences, artist_song, rating, "X40.crew.Not.Enough":"Wheezer.Buddy.Holly")
  Ratings <- tibble(pseudonym=Rating$pseudonym, artist_song=Rating$artist_song, rating=Rating$rating)
Ratings$artist_song <- gsub('.', ' ', Ratings$artist_song)



#survey$time_submitted <- as.POSIXlt(parse_datetime(survey$time_submitted), format="%m%d%y")
```