---
title: "Music Insights"
author: "Madeline Hoshko"
date: "September 19, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
include <- function(library_name){
  if( !(library_name %in% installed.packages()) )
    install.packages(library_name) 
  library(library_name, character.only=TRUE)
}
include("tidyverse")
include("knitr")


survey <- read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences<-read.csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

First, I update the names of the columns to have a common naming style throughout and to simplify excessively long original column names. I show two possible ways to do so as we are able to use multiple ways since we are changing the names of every column.
```{r}
colnames(survey)[1]<-"time_submitted"
colnames(survey)[2]<-"pseudonym_generator"
colnames(survey)[3]<-"pseudonym"
colnames(survey)[4]<-"sex"
colnames(survey)[5]<-"academic_major"
colnames(survey)[6]<-"academic_level"
colnames(survey)[7]<-"year_born"
colnames(survey)[8]<-"instrument_list"
colnames(survey)[9]<-"artist"
colnames(survey)[10]<-"favorite_song"
colnames(survey)[11]<-"favorite_song_link"

colnames(survey) <- c("time_submitted", "pseudonym_generator", "pseudonym", "sex", "academic_major","academic_level", "year_born", "instrument_list", "artist", "favorite_song", "favorite_song_link")


colnames(preferences)[1] <- "time_submitted"
colnames(preferences)[2] <- "pseudonym"


```
Creates a person table to include information from survery of each student. Then creates a song table to include information on each song from the survey. Then does the same with a ratings table where I use gather to reorganize the data to no longer be wide. 
Person
```{r}
Person <- tibble(time_submitted=survey$time_submitted, pseudonym_generator=survey$pseudonym_generator,
                pseudonym=survey$pseudonym, sex=survey$sex, academic_major=survey$academic_major,
                academic_level=survey$academic_level, year_born=survey$year_born)

Person$academic_level <- as.factor(Person$academic_level)
Person$sex <- as.factor(Person$sex)
Person$academic_major <- as.factor(Person$academic_major)
levels(Person$academic_major)[levels(Person$academic_major)=="Computer information systems"] <- 
  "Computer Information Systems"

```

Favorite Song 
```{r}
favorite_song <- tibble(pseudonym=survey$pseudonym, title=survey$favorite_song,
                        artist=survey$artist, song_link=survey$favorite_song_link)


```

Ratings
```{r}
Rating <- gather(preferences, artist_song, rating, "X40.crew.Not.Enough":"Wheezer.Buddy.Holly")

Ratings <- tibble(pseudonym=Rating$pseudonym, artist_song=Rating$artist_song, rating=Rating$rating)
Ratings$artist_song <- str_replace_all(Ratings$artist_song, 
                                       pattern = "\t", 
                                       replacement = " ")

```

Talents
```{r}
talents <- tibble(pseudonym = survey$pseudonym, instruments = survey$instrument_list)
talents <- separate_rows(talents,-pseudonym, sep=",")
talents$instruments <- talents$instruments %>% 
                        trimws() %>% 
                        tolower() %>%
                        str_replace_all(pattern=".*piano.*","piano") %>%
                        str_replace_all(pattern=".*ukulele.*","ukulele") %>%
                        as.factor()

```

Favorite Ratings
```{r}
# Ratings$pseudonym <- as.factor(Ratings$pseudonym)
# favorite_song$pseudonym <- as.factor(favorite_song$pseudonym)
# favorite_ratings <- Ratings %>% 
#                     left_join(favorite_song, by="pseudonym") %>%
#                     filter(artist_song==paste(artist,title)) %>%
#                     select(pseudonym,artist_song,rating)

```

Plots
```{r}


ggplot(Ratings, aes(x=rating)) + geom_histogram(binwidth = 1)
ggplot(Ratings, aes(x=rating, y=pseudonym))+geom_boxplot()+theme_light()

ggplot(Ratings, aes(x=pseudonym, y=rating))+geom_bar( stat = "summary", fun.y = "mean")

```
